In my weld-seam HMI, geometry served as a shared interface: modified-DH transformations connected analytical kinematics, joint control, and OpenGL visualization. My later CR5 work exposed a different interface problem: new inference used an intermediate robot state before the preceding action chunk finished, producing unstable corrections. I therefore want a more rigorous framework for coordinating physical geometry, control, and industrial automation, rather than treating mechanical representation, software, and execution as adjacent subsystems. CUHK's MSc in Mechanical and Automation Engineering matches this progression.

Subject to availability in my intake, MAEG 5725 Control and Industrial Automation and MAEG 5755 Robotics would deepen the reasoning behind the interfaces I have implemented. MAEG 5160 Design for Additive Manufacturing would extend the HMI's software-represented geometry toward understanding how manufacturing constraints shape the physical geometry on which control and automation depend. With project approval, MAEG 5910 M.Sc. Project could bring these perspectives into one bounded prototype, traced from mechanical representation through controller behavior and system validation. My experience locating mismatches among coordinate conventions, software boundaries, and execution timing would give that work a practical foundation. This path would equip me to develop intelligent-manufacturing systems whose geometry, control logic, and verification are designed together.
