My Hermite work examines how action representations preserve trajectory structure. In the separate CR5 project, I learned that a policy command is meaningful on hardware only when synchronized visual observations, the robot's current state, and execution timing remain consistent. I can evaluate representation fidelity and trace deployment failures, but I need deeper command of how learning, dynamics, perception, and physical validation interact. NUS's MSc in Robotics offers that integrated training.

If the current offerings remain available in my intake, ME5409 Robot Dynamics and Control would strengthen my analysis of action timing and controlled motion; ME5411 Robot Vision and AI would deepen how visual observations support robot decisions; and ME5418 Machine Learning in Robotics would connect structured actions to learned policies. Subject to availability and approval, either the optional eight-unit ME5400 Robotics Project or four-unit ME5400A Robotics Project 1 could provide one supervised setting for two deliberately separate studies: representation fidelity evaluated under a specified offline codec protocol, and state-action consistency examined in distinct hardware trials. I would contribute experience with synchronized robot data, tokenizer evaluation, and short-horizon ServoP execution. This preparation would advance my goal of becoming a robotics and embodied-AI R\&D engineer who builds learned systems in which visual evidence, action semantics, and control execution remain coherent.
