My weld-seam HMI linked two-dimensional segmentation, modified-DH kinematics, joint control, and an OpenGL digital twin. It remained a prototype with fixed-pose motion rather than seam-derived planning, industrial deployment, or mixed reality. Later CR5 integration made workspace checks, synchronized sensing, and execution timing explicit on real hardware. I now need to progress from prototype geometry and visualization toward cyber-physical manufacturing systems that connect analytics, automation, and human interaction. The Hong Kong Polytechnic University (PolyU)'s MSc in Smart Manufacturing fits that progression.

If these subjects are available within my selected route, ISE5331 Optimization and Data Analytics for Industry 4.0 would help me turn manufacturing observations into defensible decisions, while ISE5321 Cyber-Physical Industry 4.0 Systems would frame the links among sensors, software, and equipment. ISE5312 Industrial Human-Robot Systems and Automation would extend my isolated robot integration toward human-aware production workflows, and ISE5322 Industrial Metaverse and Mixed Reality would provide concepts I have not yet implemented for connecting virtual representations to operational context. By exposing coordinate, data, and timing assumptions rather than hiding them inside a demonstration, I could make critical boundaries explicit in team prototypes. Applied to these subjects, that discipline would prepare me to develop intelligent-manufacturing systems whose digital and physical behavior can be evaluated together.
