Migrating an ANYmal-C navigation task made me confront how commands, observations, rewards, and termination together define mobile-robot autonomy. My CR5 work raised a complementary interface problem for manipulation: visual state and policy actions must remain meaningful while the arm moves. My separate Hermite research adds a third layer: how an offline trajectory representation defines what an interface may eventually need to carry. I now want to understand how multimodal perception, task definitions, and control should change between mobile robots and manipulators. NTU's MSc in Robotics and Intelligent Systems addresses that systems-level question.

If its resources remain available for my target intake, the published January 2027 curriculum offers a path into that question. MA6214 Autonomous Mobile Robot would extend my command and observation work into multimodal fusion, planning, and motion control. MA6212 Robotics Manipulation and Advanced Control would let me compare mobile-robot interfaces with manipulation, while MA6211 AI and Machine Learning Fundamentals for Robotics would help me examine how learned action representations meet both sets of task definitions. If approved, MA6215 Robotics Projects in the coursework-only route could support a prototype comparing how one representation interfaces with mobile planning and manipulator execution under different observation and completion rules. I would contribute experience from navigation migration, offline action-tokenizer research, and CR5 deployment, then apply the comparison to autonomous-system R\&D.
