In my weld-seam HMI, modified-DH transformations linked analytical kinematics, joint controls, and an OpenGL digital twin under one coordinate convention. On the CR5, eye-to-hand calibration remained an operating constraint, workspace checks bounded admissible targets, and blocking short-horizon ServoP execution preserved state-action consistency. These experiences taught me to expose limitations rather than label an integrated robot as precise or industrially deployed. I now want a stronger framework for uniting precision, sensing, control, and mechatronics in physical-system validation. HKUST's MSc in Mechanical Engineering fits that progression.

Where the current courses are offered in my intake, MESF5550 Robotics would deepen the control and robot-system reasoning behind my implementations, while MESF5560 Precision Manufacturing Technologies would strengthen how I account for manufacturing precision in mechanisms and validation. MESF5970 Smart Materials, Sensors and Transducers would broaden my understanding of sensing and actuation beyond the camera and gripper interfaces I have used. If the project is approved, MESF6950 Independent Project could bring these strands into one bounded prototype with explicit calibration, workspace, and execution tests. I would contribute cross-disciplinary experience tracing a robot from geometric representation through software commands to observed motion. This path would prepare me for robotics or intelligent-manufacturing R\&D in which mechanical design, sensing, control, and evidence are developed together.
